Exploring dimensions of biodiversity in Japanese ferns

### 2021-04-16 ms/manuscript.Rmd
Remove drake files

```{r load-data, cache = FALSE}
# NOTE: This Rmd is meant to be knit as part of the drake plan (R/plan.R).
# If using interactively, run `source("_drake.R")` first.

loadd(list = c(
  "occ_point_data_ferns",
  "occ_point_data_ferns_unfiltered",
  "biodiv_ferns_spatial",
  "k_taxonomy",
  "k_phylogeny",
  "signif_cells_protected_area",
  "protected_areas",
  "japan_shp",
  "phy_sig_results",
  "binary_sig_results",
  "traits_summary",
  "fern_traits",
  "japan_pterido_tree",
  "japan_fern_tree",
  "ppgi",
  "occ_point_data_ferns",
  "comm_ferns_full",
  "comm_ferns",
  "japan_points_raw",
  "green_list"
),
cache = ja_fern_cache)

phylo_cache <- new_cache(here::here("phylo_cache"))

loadd(list = c(
  "plastome_calibration_dates",
  "plastome_tree"
),
cache = phylo_cache)

>>>>

```{r load-data, cache = FALSE}
# NOTE: This Rmd is meant to be knit as part of the drake plan (R/plan.R).
# If using interactively, run `source("_targets.R")` first.

tar_load(c(
  "occ_point_data_ferns",
  "occ_point_data_ferns_unfiltered",
  "biodiv_ferns_spatial",
  "k_taxonomy",
  "k_phylogeny",
  "signif_cells_protected_area",
  "protected_areas",
  "japan_shp",
  "phy_sig_results",
  "binary_sig_results",
  "traits_summary",
  "fern_traits",
  "japan_pterido_tree",
  "japan_fern_tree",
  "ppgi",
  "occ_point_data_ferns",
  "comm_ferns_full",
  "comm_ferns",
  "japan_points_raw",
  "green_list"
))

phylo_cache <- drake::new_cache(here::here("phylo_cache"))

drake::loadd(list = c(
  "plastome_calibration_dates",
  "plastome_tree"
),
cache = phylo_cache)
